### 2015-01-08 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo: clean up hose tests
DelCo_2014_Hose: minor update to report
DelCo_2014_Hose: Added inventor files, edited plotting script and report

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/east_structure}
\\~\\
\includegraphics[width=6in]{../Pictures/west_structure}
\caption{East (top) and West (bottom) Test Structures}
\label{fig:struct_pics}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{Drawings/PDFs/West_Structure_Test_General_1st_Floor}
\\
\includegraphics[width=6in]{Drawings/PDFs/West_Structure_Test_General_2nd_Floor}
\caption{West Structure ground floor (top) and 2$^{nd}$ floor (bottom) layouts.}
\label{fig:west_drawing_general}
\end{figure}

@@

\section{Experimental Procedure}

@@

\section{Hose Flow Tests}
\subsection{Tests 18 and 19}

Tests 18 and 19 varied in that the C side, ground level door was open for Test 18 and closed for Test 19.

Tests 18 and 19 followed identical procedures that involved flowing water into the West Structure through the C-side, ground level double doors using a 1.75 in. hose with a combination nozzle. The nozzle was used to produce three types of hose streams: a straight stream, a narrow fog stream, and a wide fog stream. Tests 18 and 19 involved three sets of experiments, one for each type of hose stream. For each set of experiments, four different application patterns were tested. First, water was applied while the hose was in a fixed position. Next, the hoseline was moved from side-to-side across the open room, creating a sweeping application pattern. Finally, the hoseline was rotated in both the clockwise and counterclockwise directions, creating clockwise and counterclockwise application patterns.

To begin each set of experiments, the combination nozzle was adjusted to produce the desired hose stream pattern. Once the nozzle was adjusted, water was applied while the hoseline was in the fixed position. After 60 seconds of water flow, the stairwell door was opened. 60 seconds after the stairwell door was opened, the C-side, second-level right door was opened, and water continued to flow for 60 more seconds. Then, the hoseline and two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.

%\subsection{DNXAXX}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A7}
%\caption{Velocity at exterior Door A, Test HOSE\_DNXAXX}
%\label{fig:HOSE_DNXAXX_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXAXX}
%\label{fig:HOSE_DNXAXX_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXAXX}
%\label{fig:HOSE_DNXAXX_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_HOSE}
%\caption{Hose pressure, Test HOSE\_DNXAXX}
%\label{fig:HOSE_DNXAXX_HOSE}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{DNXOXF}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A7}
%\caption{Velocity at exterior Door A, Test HOSE\_DNXOXF}
%\label{fig:HOSE_DNXOXF_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXOXF}
%\label{fig:HOSE_DNXOXF_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXOXF}
%\label{fig:HOSE_DNXOXF_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_HOSE}
%\caption{Hose pressure, Test HOSE\_DNXOXF}
%\label{fig:HOSE_DNXOXF_HOSE}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{DSXAXF}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A7}
%\caption{Velocity at exterior Door A, Test HOSE\_DSXAXF}
%\label{fig:HOSE_DSXAXF_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXAXF}
%\label{fig:HOSE_DSXAXF_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXAXF}
%\label{fig:HOSE_DSXAXF_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_HOSE}
%\caption{Hose pressure, Test HOSE\_DSXAXF}
%\label{fig:HOSE_DSXAXF_HOSE}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{DSXOXF}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A7}
%\caption{Velocity at exterior Door A, Test HOSE\_DSXOXF}
%\label{fig:HOSE_DSXOXF_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXOXF}
%\label{fig:HOSE_DSXOXF_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXOXF}
%\label{fig:HOSE_DSXOXF_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_HOSE}
%\caption{Hose pressure, Test HOSE\_DSXOXF}
%\label{fig:HOSE_DSXOXF_HOSE}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{IXAOXX}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A6}
%\caption{Velocity at interior Door CD, Test HOSE\_IXAOXX}
%\label{fig:HOSE_IXAOXX_BDP_A6}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A7}
%\caption{Velocity at exterior Door A, Test HOSE\_IXAOXX}
%\label{fig:HOSE_IXAOXX_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test HOSE\_IXAOXX}
%\label{fig:HOSE_IXAOXX_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test HOSE\_IXAOXX}
%\label{fig:HOSE_IXAOXX_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_HOSE}
%\caption{Hose pressure, Test HOSE\_IXAOXX}
%\label{fig:HOSE_IXAOXX_HOSE}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{IXXAXX}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A6}
%\caption{Velocity at interior Door CD, Test HOSE\_IXXAXX}
%\label{fig:HOSE_IXXAXX_BDP_A6}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A7}
%\caption{Velocity at exterior Door A, Test HOSE\_IXXAXX}
%\label{fig:HOSE_IXXAXX_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test HOSE\_IXXAXX}
%\label{fig:HOSE_IXXAXX_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test HOSE\_IXXAXX}
%\label{fig:HOSE_IXXAXX_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_HOSE}
%\caption{Hose pressure, Test HOSE\_IXXAXX}
%\label{fig:HOSE_IXXAXX_HOSE}
%\end{figure}
%
%

@@

Tests 18 and 19 varied in that the C side, ground level door was open for Test 18 and closed for Test 19.

Tests 18 and 19 followed identical procedures that involved flowing water into the West Structure through the C-side, ground level double doors using a 1.75 in. hose with a combination nozzle. The nozzle was used to produce three types of hose streams: a straight stream, a narrow fog stream, and a wide fog stream. Tests 18 and 19 involved three sets of experiments, one for each type of hose stream. For each set of experiments, four different application patterns were tested. First, water was applied while the hose was in a fixed position. Next, the hoseline was moved from side-to-side across the open room, creating a sweeping application pattern. Finally, the hoseline was rotated in both the clockwise and counterclockwise directions, creating clockwise and counterclockwise application patterns.

To begin each set of experiments, the combination nozzle was adjusted to produce the desired hose stream pattern. Once the nozzle was adjusted, water was applied while the hoseline was in the fixed position. After 60 seconds of water flow, the stairwell door was opened. 60 seconds after the stairwell door was opened, the C-side, second-level right door was opened, and water continued to flow for 60 more seconds. Then, the hoseline and two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014BDP_A10_8_All_Streams}
\caption{Velocity at Ceiling Level of Stairwell Door, Test 18, All Streams}
\label{fig:Test_18_West_063014_SS_BDP_A10}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014BDP_A10_8_CW_vs_CCW}
\caption{Velocity at Ceiling Level of Stairwell Door, Test 18, All Streams, CW vs. CCW}
\label{fig:Test_18_West_063014_SS_BDP_A10}
\end{figure}

@@

%
%
%\section{Fire Tests}
%
%\subsection{FIRE\_FA2S1C1NCX1\_1}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A7}
%\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A7}
%\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A8}
%\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A9}
%\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_GAS}
%\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_GAS}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_HF}
%\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_HF}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A1}
%\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A1}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A2}
%\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A2}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A3}
%\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A3}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A4}
%\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A4}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A5}
%\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A5}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{FIRE\_FA2S1C1NCX1\_2}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A7}
%\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A7}
%\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A8}
%\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A9}
%\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_GAS}
%\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_GAS}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_HF}
%\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_HF}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A1}
%\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A1}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A2}
%\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A2}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A3}
%\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A3}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A4}
%\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A4}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A5}
%\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A5}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{FIRE\_FA2S1C1NCX1\_3}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A7}
%\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A7}
%\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A8}
%\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A9}
%\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_GAS}
%\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_GAS}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_HF}
%\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_HF}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A1}
%\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A1}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A2}
%\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A2}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A3}
%\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A3}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A4}
%\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A4}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A5}
%\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A5}
%\end{figure}
%
%
%\clearpage

@@

\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,references}

>>>>

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/east_structure}
\\~\\
\includegraphics[width=6in]{../../Figures/west_structure}
\caption{East (top) and West (bottom) Test Structures}
\label{fig:struct_pics}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Test_General_1st_Floor}
\\
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Test_General_2nd_Floor}
\caption{West Structure first floor (top) and second floor (bottom) layouts.}
\label{fig:west_general_plan}
\end{figure}

@@

\section{Experimental Procedure}
Tests 18 and 19 varied in that the first floor rear door was opened for Test 18 (Fig. \ref{fig:test_18_plan}) and closed for Test 19 (Fig. \ref{fig:test_19_plan}).

Tests 18 and 19 followed identical procedures that involved flowing water into the West Structure through the first floor double doors using a 1.75 in. hose with a combination nozzle. The nozzle was used to produce three types of hose streams: a straight stream, a narrow fog stream, and a wide fog stream. Tests 18 and 19 involved three sets of experiments, one for each type of hose stream. For each set of experiments, four different application patterns were tested. First, water was applied while the hose was in a fixed position. Next, the hoseline was moved from side-to-side across the open room, creating a sweeping application pattern. Finally, the hoseline was rotated in both the clockwise and counterclockwise directions, creating clockwise and counterclockwise application patterns.

To begin each set of experiments, the combination nozzle was adjusted to produce the desired hose stream pattern. Once the nozzle was adjusted, water was applied while the hoseline was in the fixed position. After 60 seconds of water flow, the stairwell door was opened. 60 seconds after the stairwell door was opened, the front right door on the second floor was opened, and water continued to flow for 60 more seconds. Then, the hoseline and two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_18_1st_Floor}
\\
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_18_2nd_Floor}
\caption{West Structure first floor (top) and second floor (bottom) layouts for Test 18. Both double doors and the rear door were open on the first floor for the duration of the test. On the second floor, the stairwell door and front right door were opened and closed during the experiments, while the rear door and front left door were in the closed position throughout the entire test.}
\label{fig:test_18_plan}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_19_1st_Floor}
\\
\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_19_2nd_Floor}
\caption{West Structure first floor (top) and second floor (bottom) layouts for Test 19. Both double doors were open and the rear door was closed on the first floor for the duration of the test. On the second floor, the stairwell door and front right door were opened and closed during the experiments, while the rear door and front left door were in the closed position throughout the entire test.}
\label{fig:test_19_plan}
\end{figure}

@@

\section{Hose Flow Tests}

@@

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014BDP_A10_8_All_Streams}
\caption{Velocity at Ceiling Level of Stairwell Door, Test 19, All Streams}
\label{fig:Test_19_West_063014_SS_BDP_A10}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014BDP_A10_8_CW_vs_CCW}
\caption{Velocity at Ceiling Level of Stairwell Door, Test 19, All Streams, CW vs. CCW}
\label{fig:Test_19_West_063014_SS_BDP_A10}
\end{figure}

@@

@@

\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}
